ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/figure_p.tex
Reorganise figures
Caption

\begin{figure*}[ht]
  % \vspace{-8pt}
   \begin{minipage}[b]{0.48\textwidth}
  % \begin{center}

    \subfigure[Aligned MHC pangenome]{
      \includegraphics[width=\textwidth]{fig/mhc-align.eps}
      \label{subfig1}
    }
    \vspace{-11pt}
    \newline
    \subfigure[Consensus MHC pangenome]{
      \includegraphics[width=\textwidth]{fig/mhc-pangenome.eps}
      \label{subfig2}
    }
            \caption{(b) Visualizing the Major Histocompatibility Complex
                (MHC) \textit{locus} pangenome. A) \cmd{odgi viz} 1D visualization
                of 8 haploid, phased human genome assemblies plus the chm13
                and GRCh38 reference genomes. Graph nodes’ are arranged
                from left to right. The colored bars represent the
                linearized renderings of the embedded paths versus the nodes
                in a binary matrix. The black lines under the paths are the
                links, which represent the graph topology. B)
                Bandage~\citep{26099265} representation of the graph
                topology of a consensus MHC pangenome graph representing
                only variations bigger than 100 bps. Gene labels were
                applied exploiting \cmd{odgi position} to liftover gene
                coordinates from the full graph into the consensus graph.  }

>>>>

\begin{figure*}[ht]
  \vspace{-10pt}
   \begin{minipage}[b]{\textwidth}
  % \begin{center}

    \subfigure[aligned MHC pangenome]{
      \includegraphics[width=.48\textwidth]{fig/mhc-align.eps}
      \label{subfig1}
    }
    \vspace{-11pt}
    % \newline
    \subfigure[consensus MHC pangenome]{
      \includegraphics[width=.48\textwidth]{fig/mhc-pangenome.eps}
      \label{subfig2}
    }
    \caption{Examples of output generated by \odgi\ visualizing the
      Major Histocompatibility Complex (MHC) \textit{locus}. (a)
      \cmd{odgi viz} projection of full MHC of eight haploid phased
      human genome assemblies, plus the chm13 cell line and GRCh38
      reference genomes as supplied by the human reference pangenome
      consortium\citep{RPC}. The coloured bars represent the
      linearized paths --- representing individuals --- as a zoomed
      out multi-sequence alignment. The black lines at the bottom
      represent the graph topology. (b) consensus representation of
      the graph of the same MHC assemblies showing variations larger
      than $100$ base pairs. The gene label coordinates were super
      imposed by \cmd{odgi position} from GRCh38. Figure genrated by
      the Bandage tool\citep{26099265} }
